\VideoClassification[column=3, colour=blue]

%---------------------------------------------------------


\section{Introduction To Data Management and Data Warehouse}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Chapter Objectives}

\begin{itemize}[<+->]
	\item Be familiar with data management life-cycle.
	\item Understand the data abstraction and the data layer.
	\item Motivation to DWH.
	\item What are the different types of DWH?
	\item Usecases for DWH. How is it different from the operational DB?
	\item Explain the data Encoding and Formats.
	\item Show what the challenges of building a DWH are?
	\item What are the data modeling and its design?
\end{itemize}
%https://opentextbc.ca/dbdesign01/chapter/chapter-5-data-modelling/
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Data Management}

\begin{frame}
\frametitle{Data Management}

\begin{itemize}[<+->]
\item Data are a product.
\item Data product has a life-cycle as following (simplified):
\begin{itemize}[<+->]
	\item \textbf{Question}, Idea, or service.
	\item \textbf{Identify} the source of information and the data type.
	\item \textbf{Document} all details regarding the data including quality, security, efficiency, and access (consideration during the cycle).
	\item Delivery automation (Tools and Process). AKA \textbf{DevOps} cycle.
	\item Data Architecture (model design and rules).
	\item \textbf{Extraction}, \textbf{Transformation}, and \textbf{Loading} Process.
	\item Business Intelligence (\textbf{BI}) or data discovery (continues process).
	\item \textbf{Integration} and publishing.
	\item Data retention or \textbf{archiving} process \forexample (Hot or Cold storage).
\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Data Management Life-Cycle}
\scalebox{0.9}{

\smartdiagramset{circular distance=3.5cm,
font=\scriptsize,
%				text width=1cm,
module minimum width=2cm,
circular distance =3.4cm,
module minimum height=.1cm,
arrow tip=to}
\smartdiagram[circular diagram]{Archiving,Idea, Identify, Document, 				
DevOps, Arch.,ETL, BI, Integration}
}
\end{frame}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
% !TeX root = ../main.tex
%%% TeX-engine: xetex
%%% End: