%---------------------------------------------------------
\VideoClassification[column=2, colour=blue]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Introduction to DWH}

\subsubsection{Motivation to the Data Warehouse (DWH)}
\begin{frame}
\frametitle{Motivation to the Data Warehouse (DWH)}
	\begin{itemize}[<+->]
		\item Data could be a product for some companies.
		\item It could be decision support for other products or businesses.
		\item It could be reporting the results after passing the data life-cycle from storage (Database).
		\item Some challenges are facing the people who work on data management backend:
			\begin{itemize}[<+->]
				\item Performance,
				\item Integration,
				\item and Applying analytical functions. %Moving average
			\end{itemize}
		\item Vendors who are working on solving the above challenges are creating their product of DWH. Their ultimate goal is to optimize the above points.
	\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[c]
\frametitle{Motivation to the Data Warehouse (DWH)}

\begin{definition}[What is Data Warehousing?] A DWH is a technique for collecting and managing data from varied sources to \textbf{provide meaningful business insights}. It is a blend of technologies and components which aids the strategic use of data.%\footnotemark
\end{definition}

%REF
Inmon Bill gave the real concept. He is considered the father of the DWH. He had written about a variety of topics for building, usage, and maintenance of the warehouse \& the Corporate Information Factory

%\footnotetext{The definition mentioned in this slides copied from  \href{https://www.guru99.com/data-warehousing.html\#2}{guru99.com} }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Motivation to the Data Warehouse (DWH)}

\begin{itemize}[<+->]
	\item The DWH is not a product but an environment.
	\item It is a process of transforming data into information and make it available to users in a \textbf{timely manner} to make a difference.
	\item It is an architectural construct of an information system that provides users with current and historical decision support information which is difficult to access or present in the traditional operational data store.
	\item The DWH is the core of the BI system built for data analysis and reporting.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Motivation to the Data Warehouse}

Other names for the Data warehouse system:

\begin{wideitemize}
\item Decision Support System (DSS).
\item Business Intelligence Solution.
\item Executive Information System.
\item Management Information System.
\item Analytic Application.
\item Data Warehouse.

\end{wideitemize}


\end{frame}
